Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints

### 2025-05-02 manuscript.tex
new measurement result

The proposed CONAC was validated via real-time experiment on a two-link manipulator.

@@

To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
The OpenCR1.0 \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
\color{red}
The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two @@@@@ servos. 
The servos were controlled using the OpenCR1.0 board, which was connected to a computer via USB. 
The reference trajectory was generated using the same method as in the numerical simulation.
\color{black}

% ------------------------------------
% Robot Model and Ref. Trajectory
% ------------------------------------
The two-link manipulator model is depicted in Fig.~\ref{fig:robot:model}, adapted from \cite{Markus:2013aa}. 
\MSRY{CORRECT HERE}
The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, and for the numerical validation, the parameters are assumed to be constant such that $\rbM=\mydiag([m_1,m_2])$, $\rbVm=\mydiag([b_1,b_2])$, and $\rbF=\mydiag([f_{c_1},f_{s_1},f_{c_2},f_{s_2}])$,
where the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p,{f_c}_p$ and ${f_s}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous friction coefficient, coulomb friction coefficient, and static friction coefficient, respectively, for link $p\in[1,2]$.
The values of the system model parameters are provided in Table~\ref{table:system:params}.

@@

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
    %   \includegraphics
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % fig/Fig1.pdf
        src/script_simulation/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/script_simulation/figures/compare/Fig11.eps
        src/script_simulation/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\rbu$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights ${\estwth}_i$.]{
        % \includegraphics
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            % fig/Fig7.pdf
            src/script_simulation/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  Simulation results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

\begin{figure}[t]
    \centering
    \subfloat[Control input $\tau$ in time interval from $19$ s to $21$ s (bird's eye view).]{
    % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig6.eps
        }%
        \label{fig:ctrl:result:scope:control}}
        \vfill
    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig8.eps
        }%
        \label{fig:ctrl:result:scope:beta}}
        \vfill
    \subfloat[Auxiliary states in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig9.eps
        }%
        \label{fig:ctrl:result:scope:aux}}
  \caption{
    Constraint handling process of (C$_1$) (blue), (C$_2$) (cyan), and (C$_3$) (gray) in time interval from $19$ s to $21$ s.
  }
\label{fig:ctrl:result:scope}
\end{figure}

@@

% ------------------------------------
% Norm of error in Episode 1: 
% C1 r1 ep1: 0.389
% C1 r2 ep1: 0.426
% C2 r1 ep1: 0.403
% C2 r2 ep1: 0.456
% C3 r1 ep1: 0.370
% C3 r2 ep1: 0.427
% Norm of error in Episode 2: 
% C1 r1 ep2: 0.155
% C1 r2 ep2: 0.066
% C2 r1 ep2: 0.191
% C2 r2 ep2: 0.094
% C3 r1 ep2: 0.141
% C3 r2 ep2: 0.083
% Improvement in Episode 2: 
% C1 r1: 0.602
% C1 r2: 0.845
% C2 r1: 0.527
% C2 r2: 0.793
% C3 r1: 0.619
% C3 r2: 0.805
% ------------------------------------
\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Quantitative comparison of performances' $L_2$ norm.}
    \centering
    \begin{tabular}{c c c c c}
    \hline
		& \multicolumn{4}{c}{\textbf{Episode 1}} \\
    \hline
	\hline 
		& (C$_1$) & (C$_2$) & (C$_3$) & (C$_4$) \\
	\hline
		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.370$ \\ 
	\hline
        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.370$ \\
	\hline
        & \multicolumn{4}{c}{\textbf{Episode 2}} \\
    \hline
    \hline
        & (C$_1$) & (C$_2$) & (C$_3$) & (C$_4$) \\
	\hline
		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.370$ \\ 
	\hline
        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.370$ \\
    \hline
    \end{tabular}
    \label{tab:sim:L2}
\end{table}

@@

\begin{figure}[t]
    \centering
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/Fig10.eps
        }%
    \caption{
        Computational time of CONAC and CONAC-AUX. 
    }
    \label{fig:ctrl:real:result:cmp:time}
  \end{figure}

>>>>

@@

To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
\color{red}
The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two @@@@@ servos. 
The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the servos via controller area network (CAN) communication.
\color{black}
The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, the estimated system parameters are provided in Table~\ref{table:system:params}.

@@

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
    %   \includegraphics
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % fig/Fig1.pdf
        src/measurement/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/measurement/figures/compare/Fig11.eps
        src/measurement/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\rbu$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights ${\estwth}_i$.]{
        % \includegraphics
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            % fig/Fig7.pdf
            src/measurement/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  Simulation results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

\begin{figure}[t]
    \centering
    \subfloat[Control input $\tau$ in time interval from $19$ s to $21$ s (bird's eye view).]{
    % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig6.eps
        }%
        \label{fig:ctrl:result:scope:control}}
        \vfill
    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig8.eps
        }%
        \label{fig:ctrl:result:scope:beta}}
        \vfill
    \subfloat[Auxiliary states in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig9.eps
        }%
        \label{fig:ctrl:result:scope:aux}}
  \caption{
    Constraint handling process of (C$_1$) (blue), (C$_2$) (cyan), and (C$_3$) (gray) in time interval from $19$ s to $21$ s.
  }
\label{fig:ctrl:result:scope}
\end{figure}

@@

% ------------------------------------
% Norm of error in Episode 1: 
% C1 e1 ep1: 0.025
% C1 e2 ep1: 0.023
% C2 e1 ep1: 0.022
% C2 e2 ep1: 0.011
% C3 e1 ep1: 0.023
% C3 e2 ep1: 0.013
% C4 e1 ep1: 0.024
% C4 e2 ep1: 0.013
% Norm of error in Episode 2: 
% C1 e1 ep2: 0.008
% C1 e2 ep2: 0.003
% C2 e1 ep2: 0.008
% C2 e2 ep2: 0.002
% C3 e1 ep2: 0.008
% C3 e2 ep2: 0.004
% C4 e1 ep2: 0.020
% C4 e2 ep2: 0.004
% Improvement in Episode 2: 
% C1 e1: 0.700
% C1 e2: 0.884
% C2 e1: 0.631
% C2 e2: 0.769
% C3 e1: 0.637
% C3 e2: 0.728
% C4 e1: 0.185
% C4 e2: 0.671
% ------------------------------------
\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Quantitative comparison of performances' $L_2$ norm.}
    \centering
    \begin{tabular}{c c c c c}
    \hline
		& \multicolumn{4}{c}{\textbf{Episode 1}} \\
    \hline
	\hline 
		& (C$_1$) & (C$_2$) & (C$_3$) & (C$_4$) \\
	\hline
		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.370$ \\ 
	\hline
        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.370$ \\
	\hline
        & \multicolumn{4}{c}{\textbf{Episode 2}} \\
    \hline
    \hline
        & (C$_1$) & (C$_2$) & (C$_3$) & (C$_4$) \\
	\hline
		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.370$ \\ 
	\hline
        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.370$ \\
    \hline
    \end{tabular}
    \label{tab:sim:L2}
\end{table}

@@

\begin{figure}[t]
    \centering
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig10.eps
        }%
    \caption{
        Computational time of CONAC and CONAC-AUX. 
    }
    \label{fig:ctrl:real:result:cmp:time}
  \end{figure}
